A novell interest management algorithm for distributed simulations of MMGs

### 2008-04-30 textos/dsrt/engaoi.tex
eng

Foram executadas diversas simulações, com o objetivo de comparar os algoritmos de gerenciamento de interesse apresentados. O número de avatares presentes no ambiente foi uma das variáves analisadas, para verificar a escalabilidade. Os algoritmos comparados foram os baseados em círculo, círculo com atenuação, ângulo de visão e o algoritmo proposto, \malg. Para demonstrar o quanto cada um destes reduz o tráfego, foram feitas simulações também em que não é empregado nenhum tipo de gerenciamento de interesse, e o servidor envia para o cliente atualizações de estado de todas as outras entidades do jogo.

@@

Apenas usando diferentes freqüências de atualização no gerenciamento de interesse baseado em círculo, reduziu-se em 41.59\% a largura de banda de envio utilizada em média pelo servidor por cliente. A utilização máxima de largura de banda também foi reduzida, em 36.19\%. Estes valores representam a média de redução de uso de largura de banda para os diferentes números de clientes.

>>>>

Several simulations were executed, in order to compare the described interest management algorithms. The number of avatars in the environment was one of the variables analyzed, to verify the scalability. The algorithms compared were the ones with circle, circle with attenuation and field of view based area of interest and the proposed algorithm, \malg. To demonstrate how each one of these reduces traffic, simulations in which no type of interest management was used - and the server sent to the client state updates of all entities in the environment - were also performed.

@@

Just by using different update frequencies with circular area based interest management, the average upload bandwidth usage by the server decreased 41.59\%. The maximum upload bandwidth usage was also reduced, decreasing 36.19\%. These values represent the average usage reduction among all different numbers of avatars, compared to the circular area of interest algorithm with no frequency update attenuation.

Regarding the proposed algorithm, \malg, it has been obtained an upload bandwidth usage reduction of 63.51\% and 33.58\%, respectively compared to the circular area of interest and the field of view based algorithms. The maximum upload bandwidth usage was also reduced, decreasing 63.51\% and 33.58\%, comparing to the same algorithms. Table \ref{tab_summary} shows the percentage of economy-wide average, maximum and average banda with the algorithm \ malg compared with other algorithms presented.
